Dependent Object Types

### 2012-09-13 doc/fool/article.tex
put the redex generated example in
comment out wip ex section
minor clarifications

\infrule[\textsc{vdecl}]
{\Gamma \ts v \typ {V'} \spcomma {V'} \sub V}
{\Gamma \ts l = v \typ \ldecl l V}

\infrule[\textsc{mdecl}]
{\Gamma \ts S \wfe\\
 \Gamma \envplus{x : S} \ts t \typ {T'} \spcomma {T'} \sub T}
{\Gamma \ts m(x) = t \typ \mdecl m S T }

@@

Two sub-sorts of terms are values $v$, which consist of just
variables, and paths $p$ which consist of just variables and field
selections.

@@

\figref{dot-sub} defines the subtyping judgement $\Gamma \ts S
\sub T$ which states that in environment $\Gamma$ type $S$ is a
subtype of type $T$. Subtyping is regular wrt $\nswfe$: if
type $S$ is a subtype of type $T$, then $S$ and $T$ are well-formed
and expanding. Though this regularity limits our calculus to
$\nswfe$-types, this limitation allows us to show that subtyping is
transitive, as discussed in section~\ref{dot-preservation}.

@@

\subsubsection{Why limit the calculus to $\nswfe$-types?}

@@

>>>>

\infrule[\textsc{vdecl}]
{\Gamma \ts v \typ {V'} \spcomma {V'} \sub V}
{\Gamma \ts (l = v) \typ (\ldecl l V)}

\infrule[\textsc{mdecl}]
{\Gamma \ts S \wfe\\
 \Gamma \envplus{x : S} \ts t \typ {T'} \spcomma {T'} \sub T}
{\Gamma \ts (m(x) = t) \typ (\mdecl m S T) }

@@

Two sub-sorts of terms are values and paths. Values $v$ consist of
just variables. Paths $p$ consist of just variables and field
selections.

@@

\figref{dot-sub} defines the subtyping judgement $\Gamma \ts S
\sub T$ which states that in environment $\Gamma$ type $S$ is a
subtype of type $T$. Subtyping is regular wrt $\nswfe$: if
type $S$ is a subtype of type $T$, then $S$ and $T$ are well-formed
and expanding. Though this regularity limits our calculus to
$\nswfe$-types, this limitation allows us to show that subtyping is
transitive, as discussed in section~\ref{dot-variants-why-wfe}.

@@

\subsubsection{Why limit the calculus to $\nswfe$-types?}\label{dot-variants-why-wfe}

@@

%\section{Examples}
%TODO: WIP
%
%\includegraphics[scale=0.7]{../../src/redex/ex_glb}
